% ----------------------------------------------------------
\chapter{Systematic Review of the Literature: Text Regression}\label{ap:rsl_regression_law}
% ----------------------------------------------------------

In this SRL, we focused on find papers related to the application of regression techniques on legal texts written in Portuguese language. However, such task did not succeed due to the lack of work in that matter. Thus, we applied a broader search regarding the application of regression in texts without context or language limitations.

\section{Definition of Search Questions}

The question of this search is: ``What are the regression techniques applied to texts considering any applications and languages?''

\section{Search Strategies}

The search used the following search string:

% TODO: Continue from here.
\begin{verbatim}
  ( "regression on text*"  OR  "text* regression"  OR  "regression text*"  
  OR  "regression from text*"  OR  "regression for text*" )  
  AND NOT  "logistic regression"  
\end{verbatim}



\section{Search Resources}
In this SRL, we searched on the following bases:

\begin{itemize}[noitemsep]
    \item Scopus
    \item ACM Digital Library
    \item IEEE Xplore
    \item Web of Science
\end{itemize}

\section{Selection Criteria}

Following the questions of this research, we defined a set of inclusion and exclusion criteria. The process of selection embraced the reading of title, abstract and keywords and the accordance with the criteria:

The following is the list of inclusion criteria:

\begin{itemize}[noitemsep]
    \item Published in journal or conference
    \item Involves regression applied to textual data;
    \item Involves Machine Learning or Text Mining;
    \item The techniques used are named;
    \item Empirical Work;
    \item Published from 2010 and December 2020.
\end{itemize}

And the following is the list of exclusion criteria:

\begin{itemize}[noitemsep]
    \item Work not written in Portuguese or English;
    \item Published over 10 years ago;
    \item Does not involve regression applied to textual data;
    \item Does not involve Machine Learning or Text Mining;
    \item Theoretic work.
\end{itemize}

\section{Data Extraction}
In the SRL from this section, we focused on just retrieving the regression techniques used and the application.

\section{Search Execution and Preliminary Analysis}

After applying the first search string to the knowledge base on December 1, 2020 for researches published from 2010 to December 2020, the search returned 124 documents. After reading title, abstract and keywords and applying the selection criteria, the number of papers reduced to 23.

